SPAMDA: A software tool to manage meteorological data for environmental modelling

### 2020-03-05 latex_manuscript/elsevier/5_Advances_in_Engineering_Software/spamda.tex
Sending to Advances in Engineering Software journal. Latex and letters files.

		This work has been partially subsidised by the projects TIN2017-85887-C2-1-P and TIN2017-90567-REDT of the Spanish Ministry of Economy and Competitiveness (MI\-NE\-CO), and FEDER funds of the European Union. We also thank to NVIDIA Corporation for the transfer of computational resources for research works.

>>>>

		This work has been partially subsidised by the projects with references TIN2017-85887-C2-1-P of the Spanish Ministry of Economy and Competitiveness (MI\-NE\-CO), UCO-1261651 of the ``Consejer\'ia de Econom\'ia, Conocimiento, Empresas y Universidad'' of the ``Junta de Andaluc\'ia'' (Spain) and FEDER funds of the European Union. We also thank to NVIDIA Corporation for the transfer of computational resources for research works.
